Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-09-10 Manuscript.Rmd
Figure renaming

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/ROIS.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
include_graphics("./Images/FB_FV_example.png")
```

@@

include_graphics("./Images/similarity_all.png")

@@

include_graphics("./Images/SW_props.png")

@@

include_graphics("./Images/thresholded.png")

@@

include_graphics("./Images/ratios.png")

@@

include_graphics("./Images/commvscorr.png")

@@

include_graphics("./Images/sulciVSfv.png")
```

@@

# Change to inflated eventually
include_graphics("./Images/braga_comparison.png")

@@

```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 1. Additional examples of individualized partitionings. The first two columns show both Fiedler vector values  and binarized communities, respectively. A common organizational principle is visible, even though it shifts topographically across individuals. The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408). The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation). The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
include_graphics("./Images/extra_examples.png")
```

@@

include_graphics("./Images/ARI_comparison.png")

@@

include_graphics("./Images/tSNR.png")
```

@@

```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 4. Visual examples of idiosyncratic organization across days and runs. Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals. The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1). Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2. As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g. subjects 100408 and 687163). Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data. This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
include_graphics("./Images/days_runs_examples.png")
```

@@

include_graphics("./Images/kmeansVSsp.png")
```

>>>>

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/FIG1.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
include_graphics("./Images/FIG2.png")
```

@@

include_graphics("./Images/FIG3.png")

@@

include_graphics("./Images/FIG4.png")

@@

include_graphics("./Images/FIG5.png")

@@

include_graphics("./Images/FIG6.png")

@@

include_graphics("./Images/FIG7.png")

@@

include_graphics("./Images/FIG8.png")
```

@@

# Change to inflated eventually
include_graphics("./Images/FIG9.png")

@@

```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 1. Additional examples of individualized partitionings. The first two columns show both Fiedler vector values  and binarized communities, respectively. A common organizational principle is visible, even though it shifts topographically across individuals. The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408). The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation). The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
include_graphics("./Images/SFIG1.png")
```

@@

include_graphics("./Images/SFIG2.png")

@@

include_graphics("./Images/SFIG3.png")
```

@@

```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 4. Visual examples of idiosyncratic organization across days and runs. Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals. The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1). Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2. As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g. subjects 100408 and 687163). Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data. This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
include_graphics("./Images/SFIG4.png")
```

@@

include_graphics("./Images/SFIG5.png")
```
